---
title: 'Scenarios for e-mobility Survey'
author: "[Orhan Aktaş](https://www.linkedin.com/in/orhanaktas/)"
date: "4 July 2022"
output:
  html_document:
    theme: flatly
    df_print: paged
    number_sections: true
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

```{r libraries, include=FALSE}
library(DoE.base)
library(formattable)
library(tidyverse)
library(reactablefmtr)
```

# The topics that are needed to be decided

## Alternative Designs

-   Fractional factorial design

-   Full factorial design (with blocks)

## Variable Types

-   Categorical

-   Numeric

# Creating Experimental Designs

defining variables for each type

```{r}
categorical_fctr_def<-list(
    pri_car = c("status quo", "limited"),
    n_transfer = c("transfer free", "one transfer"),
    freq = c("status quo", "increased"),
    fare = c("status quo", "higher")
  )

numeric_fctr_def<-list(
    park_price = c("10tl", "20tl"),
    n_transfer = c("0", "1"),
    freq = c("10min", "5min"),
    fare = c("6tl", "9tl")
  )
```

## Fractional factorial design

creation of scenarios

```{r}
plan <-
  oa.design(factor.names = categorical_fctr_def) %>%
  as_tibble() %>%
  mutate(scenario = row_number()) %>%
  relocate(scenario)
```

table of scenarios

```{r}
plan
```

coloured table of scenarios

```{r}

plan %>%

  formattable(list(
    pri_car = formatter(
      "span",
      style = x ~ ifelse(x == "status quo",
                         style(color = "red",font.weight = "bold"),
                         style(color = "green",font.weight = "bold")
                         )
    ),
    n_transfer = formatter(
      "span",
      style = x ~ ifelse(x == "one transfer",
                         style(color = "red",font.weight = "bold"),
                         style(color = "green",font.weight = "bold")
                         )
    ),
    freq = formatter(
      "span",
      style = x ~ ifelse(x == "status quo",
                         style(color = "red",font.weight = "bold"),
                         style(color = "green",font.weight = "bold")
                         )
    ),
    fare = formatter(
      "span",
      style = x ~ ifelse(x == "status quo",
                         style(color = "red",font.weight = "bold"),
                         style(color = "green",font.weight = "bold")
                         )
    )
    
    
    ))
```

## Full factorial design (with blocks)

creation of scenarios

```{r}
plan<-fac.design(factor.names=categorical_fctr_def, blocks=2, seed=12345) %>% as_tibble
```

coloured table of scenarios

```{r}

plan %>%

  formattable(list(
    Blocks = formatter(
      "span",
      style = x ~ ifelse(x == 1,
                         style(color = "orange",font.weight = "bold"),
                         style(color = "purple",font.weight = "bold")
                         )
    ),
    
    pri_car = formatter(
      "span",
      style = x ~ ifelse(x == "status quo",
                         style(color = "red",font.weight = "bold"),
                         style(color = "green",font.weight = "bold")
                         )
    ),
    n_transfer = formatter(
      "span",
      style = x ~ ifelse(x == "one transfer",
                         style(color = "red",font.weight = "bold"),
                         style(color = "green",font.weight = "bold")
                         )
    ),
    freq = formatter(
      "span",
      style = x ~ ifelse(x == "status quo",
                         style(color = "red",font.weight = "bold"),
                         style(color = "green",font.weight = "bold")
                         )
    ),
    fare = formatter(
      "span",
      style = x ~ ifelse(x == "status quo",
                         style(color = "red",font.weight = "bold"),
                         style(color = "green",font.weight = "bold")
                         )
    )
    
    
    ))
```
